|

### 2021-12-24 paper/dcpo_demsupport.Rmd
modify notation of beta and variance in MOC. @fsolt @sammo3182

2. For each analysis model, we run the model with $\theta^{t}$, and $w$, and save the coefficient estimates $\beta^{t}$ and variance-covariance matrix of $\hat{\beta^{t}}$, $\hat{V^{t}}$, both of which change due to the uncertainty in $\theta$.

3. We sample $\tilde{\beta^{t}}$ from the multivariate normal density with mean vector $\beta^{t}$ and variance-covariance matrix $V^{t}$.

>>>>

2. For each analysis model, we run the model with $\theta^{t}$, and $w$, and save the coefficient estimates $\hat{\beta^{t}}$ and variance-covariance matrix of $\hat{\beta^{t}}$, $\hat{V^{t}}$, both of which change due to the uncertainty in $\theta$.

3. We sample $\tilde{\beta^{t}}$ from the multivariate normal density with mean vector $\hat{\beta^{t}}$ and variance-covariance matrix $\hat{V^{t}}$.
